\documentclass[aspectratio=169,12pt,t]{beamer}
\usepackage{graphicx}
\setbeameroption{hide notes}
\setbeamertemplate{note page}[plain]
\usepackage{listings}
\usepackage{ulem}

\input{LaTeX/header.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% end of header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% title info
\title{Reviewing papers}
\subtitle{}
\author{\href{https://kbroman.org/BMI883}{\tt kbroman.org/BMI883} }
\institute{}
\date{\small \hspace{3in} Karl Broman \\
  \hspace{3in} \href{https://kbroman.org}{\color{foreground}
    \small \tt kbroman.org}}



\begin{document}


% title slide
{
\setbeamertemplate{footline}{} % no page number here
\frame{
  \titlepage
} }



\begin{frame}{Review content}

\bbi
\item Is it interesting/important?
\item Is it correct?
\item Is it understandable?
\item How could it be improved?
  \bi
\item necessary vs recommended changes
  \ei
  \ei

\end{frame}




\begin{frame}{Mechanics}


  \bbi
\item Comments to the authors
  \bi
\item No mention of recommendation
\item Paragraph describing the work
\item Paragraph summarizing review
\item Separate major and minor points
\item Don't leave anything out
\item Point to specific examples from the text
\item Authors do things differently than you; {\hilit does it matter}?
\item Use the ``sandwich'' method for constructive criticism
  \ei
\item Comments to the editor
  \bi
  \item Recommendation: accept, minor revisions, major revisions, reject
  \item Summary of criticism, but no need to repeat
  \item (vent a bit?)
  \ei
  \ei

\end{frame}



\begin{frame}{Questions}


  \bbi
\item Why review papers?
\item Who is the reviewer working for?
\item Should reviews be open?
\item Should reviews be non-anonymous?
  \ei

\end{frame}






\end{document}
